An OpenCL-based tridiagonal solver for evaluation of compact finite differences on parallel architectures

### 2015-12-02 presentation/compact-finite-difference-application.tex
updates

Solving a tridiagonal system of size
$mP$, split among $P$ processes:

@@

\begin{frame}
\frametitle{Compact finite difference on multi-GPU system}
\footnotesize
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{enumerate}
\item Computing RHS for all local grid points - \textbf{requires communication}
\begin{itemize}
    \footnotesize
    \item halo swaps with neighbouring GPUs
    \item pointwise stencil
\end{itemize}
\item Solving local tridiagonal systems - no communication
\item Assembling and solving reduced tridiagonal systems - \textbf{requires communication}
\begin{itemize}
    \footnotesize
    \item global communication along line of GPUs
    \item produces interleaved tridiagonal sysems - pThomas algorithm
\end{itemize}
\item Summing solutions from steps 2 and 3 - no communication
\begin{itemize}
    \footnotesize
    \item pointwise sum
\end{itemize}
\item For other coordinate directions: \emph{local} permutation of data
\end{enumerate}
\end{column}
\begin{column}{0.5\textwidth}
\only<1>{\includegraphics[width=150px]{img/rhs-halos.eps}}
\only<2>{\includegraphics[width=150px]{img/constructing-reduced-system.eps}}
\end{column}
\end{columns}
\end{frame}

>>>>

Solving a tridiagonal system of size
$mP$, split among $P$ processes (Mattor et al., 1995):

@@

\begin{frame}
\frametitle{Compact finite difference on multi-GPU system}
\footnotesize
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{enumerate}
\item Computing RHS for all local grid points - \textbf{requires communication}
\begin{itemize}
    \footnotesize
    \item halo swaps with neighbouring GPUs
    \item pointwise stencil
\end{itemize}
\item Solving local tridiagonal systems - no communication
\item Assembling and solving reduced tridiagonal systems - \textbf{requires communication}
\begin{itemize}
    \footnotesize
    \item global communication along line of GPUs
    \item produces interleaved tridiagonal sysems - pThomas algorithm
\end{itemize}
\item Summing solutions from steps 2 and 3 - no communication
\begin{itemize}
    \footnotesize
    \item pointwise sum
\end{itemize}
\item For other coordinate directions: \emph{local} permutation of data
\end{enumerate}
\end{column}
\begin{column}{0.5\textwidth}
\only<1>{\includegraphics[width=175px]{img/rhs-halos.eps}}
\only<2>{\includegraphics[width=175px]{img/constructing-reduced-system.eps}}
\end{column}
\end{columns}
\end{frame}
